`flippant` -- An `R` package for the automated analysis of dithionite scramblase

### 2015-09-21 inst/manuscript/manuscript.rmd
Start work on summary;

```{r, echo = FALSE}
library(flippant, quietly = TRUE)
library(grid, quietly = TRUE)
library(magrittr, quietly = TRUE)
library(multipanelfigure, quietly = TRUE)
library(stringi, quietly = TRUE)
flippant_dependencies <- packageDescription("flippant",fields=c("Depends","Imports")) %>%
  unlist(use.names = FALSE) %>%
  stri_split(regex = ",", omit_empty = TRUE) %>%
  unlist(use.names = FALSE) %>%
  stri_replace_all(replacement = "", regex = "\\s*\\(.*\\)\\s*", omit_empty = TRUE) %>%
  stri_replace_all(replacement = "", regex = "\\s*", omit_empty = TRUE) %>%
  tail(n=length(.) - 1) %>%
  sort() %>%
  ( function(x){
    paste0(
      c(
        "`",
        paste0(head(x, n = length(x) - 1), collapse = "`, `"),
        "` and `",
        tail(x, n = 1),
        "`"),
      collapse = "")} )

@@

#Conclusion

>>>>

```{r, echo = FALSE}
library(flippant, quietly = TRUE)
library(grid, quietly = TRUE)
library(magrittr, quietly = TRUE)
library(microbenchmark, quietly = TRUE)
library(multipanelfigure, quietly = TRUE)
library(stringi, quietly = TRUE)
flippant_dependencies <- packageDescription("flippant",fields=c("Depends","Imports")) %>%
  unlist(use.names = FALSE) %>%
  stri_split(regex = ",", omit_empty = TRUE) %>%
  unlist(use.names = FALSE) %>%
  stri_replace_all(replacement = "", regex = "\\s*\\(.*\\)\\s*", omit_empty = TRUE) %>%
  stri_replace_all(replacement = "", regex = "\\s*", omit_empty = TRUE) %>%
  tail(n=length(.) - 1) %>%
  sort() %>%
  ( function(x){
    paste0(
      c(
        "`",
        paste0(head(x, n = length(x) - 1), collapse = "`, `"),
        "` and `",
        tail(x, n = 1),
        "`"),
      collapse = "")} )

@@

#Conclusion
```{r, echo = FALSE}
setwd(tmpDir)
analysis_timing_n <- 100
analysis_timing_function <- function(){

  scramblaseAssayTraces("inputTable.txt", timeMax = 350)
}
analysis_timing <- microbenchmark(
  analysis_timing_function(),
  times = analysis_timing_n)

analysis_timing_median <- round(
  summary(
    analysis_timing)$median,
  2)

analysis_timing_iqr <- round(
  diff(
    unlist(
      summary(analysis_timing)[c("lq", "uq")],
      use.names = FALSE)),
  2)
```
With `flippant` we present an integrated solution for data analysis in the 
context of dithionite scramblase assays. Requiring only basic familiarity with 
`R` [@r_core_team_r:_2015] as an environment for statistical computing and
graphics, scientists can quickly analyse such data and arrive at 
publication-grade graphics that offer extensive facilities for individual 
optimization and adaptation [@wickham_ggplot2_2009]. On a system running `Linux`
and `R` version `r paste(R.version[c("major","minor")], collapse = ".")`, the
statements generating equivalents to the plots and calculations presented here
take a mere `r analysis_timing_median` seconds (IQR: `r analysis_timing__iqr` s;
$n==`r analysis_timing_n`$).
